---
title: "Differential phospho/protein analysis - CRC Batch 1"
author: Sophie Herbst
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
Analysis date: `r Sys.Date()`

# Depends on
DIPG_FirstBatch_DataProcessing Script

```{r}
load("../Data/Cache/Xenografts_Batch1_2_DataProcessing.RData")
```

# TODO

* Do differential abudance analysis for prep batch and mass spec run

# Setup
## Load libraries and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(2022)
library(fgsea)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(DEP)
library(SummarizedExperiment)
# library(pls)
library(mdatools)
source("../../../General/Code/Analysis_Functions.R")
source("CRC_Xenografts_Batch1_Functions.R")
```

# Analysis
## DEP
### Tyrosine all
#### Each condition vs ctrl
```{r, eval=TRUE}
data_diff_ctrl_vs_E_pY <- test_diff(pY_se, type="manual", test = "E_vs_ctrl")
dep_ctrl_vs_E_pY <- add_rejections_SH(data_diff_ctrl_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_ctrl_vs_E_pY, contrast = "E_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY") )
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_ctrl_vs_E_pY, comparison = "E_vs_ctrl_diff")
```

```{r}
data_diff_EC_vs_ctrl_pY <- test_diff(pY_se, type="manual", test = "EC_vs_ctrl")
dep_EC_vs_ctrl_pY <- add_rejections_SH(data_diff_EC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_ctrl_pY, contrast = "EC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY") )
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff")
```

```{r, eval=FALSE}
Plot_Enrichment_Single_Pathway(dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff", 
                               pw = "Epigenetic regulation of gene expression")
```

```{r}
data_diff_EBC_vs_ctrl_pY <- test_diff(pY_se, type="manual", test = "EBC_vs_ctrl")
dep_EBC_vs_ctrl_pY <- add_rejections_SH(data_diff_EBC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_ctrl_pY, contrast = "EBC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_ctrl_pY, comparison = "EBC_vs_ctrl_diff")
```


#### Not ctrl vs ctrl
```{r, eval=FALSE}
data_diff_vs_ctrl_pY <- test_diff_to_all_other(pY_se, control = "ctrl")
dep_vs_ctrl_pY <- add_rejections_SH(data_diff_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_vs_ctrl_pY, contrast = "not_ctrl_vs_ctrl", label_size = 2, add_names = TRUE, additional_title = "pY") )
```

```{r, fig.width=10, fig.height=10, eval=FALSE}
Return_DEP_Hits_Plots(data = pY_noNA, dep_vs_ctrl_pY, comparison = "not_ctrl_vs_ctrl_diff")
```

#### EC vs E
```{r}
data_diff_EC_vs_E_pY <- test_diff(pY_se, type = "manual", 
                              test = c("EC_vs_E"))
dep_EC_vs_E_pY <- add_rejections_SH(data_diff_EC_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_E_pY, contrast = "EC_vs_E", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_E_pY, comparison = "EC_vs_E_diff")

#data_results <- get_df_long(dep)
```

#### EBC vs EC
```{r}
data_diff_EBC_vs_EC_pY <- test_diff(pY_se, type = "manual", 
                              test = c("EBC_vs_EC"))
dep_EBC_vs_EC_pY <- add_rejections_SH(data_diff_EBC_vs_EC_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_EC_pY, contrast = "EBC_vs_EC", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_EC_pY, comparison = "EBC_vs_EC_diff")

#data_results <- get_df_long(dep)
```

#### Preps
```{r}
pY_se_preps <- pY_se

pY_se_preps$treatment <- pY_se_preps$condition
pY_se_preps$prep <- unlist(prep_l[paste0("Xenograft_", rownames(colData(pY_se_preps)) )])
pY_se_preps_comp <- pY_se_preps
pY_se_preps_comp$condition <- pY_se_preps$prep

data_diff_prep1_vs_prep2_pY <- test_diff(pY_se_preps_comp, type = "manual", 
                              test = c("prep1_vs_prep2"))
dep_prep1_vs_prep2_pY <- add_rejections_SH(data_diff_prep1_vs_prep2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_prep1_vs_prep2_pY, contrast = "prep1_vs_prep2", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_prep1_vs_prep2_pY, comparison = "prep1_vs_prep2_diff")

#data_results <- get_df_long(dep)
```

#### Runs
```{r}
pY_se_runs <- pY_se

pY_se_runs$treatment <- pY_se_runs$condition
pY_se_runs$run <- str_split(colnames(pY_se_runs), pattern = "_", simplify = TRUE)[,4]
pY_se_runs_comp <- pY_se_runs
pY_se_runs_comp$condition <- pY_se_runs$run

data_diff_Set1_vs_Set2_pY <- test_diff(pY_se_runs_comp, type = "manual", 
                              test = c("Set1_vs_Set2"))
dep_Set1_vs_Set2_pY <- add_rejections_SH(data_diff_Set1_vs_Set2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_Set1_vs_Set2_pY, contrast = "Set1_vs_Set2", label_size = 2, add_names = TRUE, additional_title = "pY") )
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_Set1_vs_Set2_pY, comparison = "Set1_vs_Set2_diff")

#data_results <- get_df_long(dep)
```


### Prep 1
#### Each condition vs ctrl 
```{r, eval=TRUE}
pY_se_prep1 <- pY_se_preps
pY_se_prep1 <- pY_se_prep1[,pY_se_prep1$prep == "prep1" ]
data_diff_ctrl_vs_E_pY <- test_diff(pY_se_prep1, type="manual", test = "E_vs_ctrl")
dep_ctrl_vs_E_pY <- add_rejections_SH(data_diff_ctrl_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_ctrl_vs_E_pY, contrast = "E_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
paste0("log2FC_Xenograft_", colnames(pY_se_prep1) )

str_remove( colnames(pY_noNA), "log2FC_Xenograft_" )
pY_noNA %>% select()
Return_DEP_Hits_Plots(data = pY_noNA , 
                      dep_ctrl_vs_E_pY, 
                      comparison = "E_vs_ctrl_diff")

Return_DEP_Hits_Plots(data = pY_noNA , 
                      dep_ctrl_vs_E_pY, 
                      comparison = "E_vs_ctrl_diff")
```

```{r}
data_diff_EC_vs_ctrl_pY <- test_diff(pY_se_prep1, type="manual", test = "EC_vs_ctrl")
dep_EC_vs_ctrl_pY <- add_rejections_SH(data_diff_EC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_ctrl_pY, contrast = "EC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff")
```

```{r, eval=FALSE}
Plot_Enrichment_Single_Pathway(dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff", 
                               pw = "Epigenetic regulation of gene expression")
```

```{r}
data_diff_EBC_vs_ctrl_pY <- test_diff(pY_se_prep1, type="manual", test = "EBC_vs_ctrl")
dep_EBC_vs_ctrl_pY <- add_rejections_SH(data_diff_EBC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_ctrl_pY, contrast = "EBC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_ctrl_pY, comparison = "EBC_vs_ctrl_diff")
```

#### EC vs E
```{r}
data_diff_EC_vs_E_pY <- test_diff(pY_se_prep1, type = "manual", 
                              test = c("EC_vs_E"))
dep_EC_vs_E_pY <- add_rejections_SH(data_diff_EC_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_E_pY, contrast = "EC_vs_E", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_E_pY, comparison = "EC_vs_E_diff")

#data_results <- get_df_long(dep)
```

#### EBC vs EC
```{r}
data_diff_EBC_vs_EC_pY <- test_diff(pY_se_prep1, type = "manual", 
                              test = c("EBC_vs_EC"))
dep_EBC_vs_EC_pY <- add_rejections_SH(data_diff_EBC_vs_EC_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_EC_pY, contrast = "EBC_vs_EC", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_EC_pY, comparison = "EBC_vs_EC_diff")

#data_results <- get_df_long(dep)
```

### Prep 2
#### Each condition vs ctrl
```{r, eval=TRUE}
pY_se_prep2 <- pY_se_preps
pY_se_prep2 <- pY_se_prep2[,pY_se_prep2$prep == "prep2" ]
data_diff_ctrl_vs_E_pY <- test_diff(pY_se_prep2, type="manual", test = "E_vs_ctrl")
dep_ctrl_vs_E_pY <- add_rejections_SH(data_diff_ctrl_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_ctrl_vs_E_pY, contrast = "E_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
paste0("log2FC_Xenograft_", colnames(pY_se_prep2) )

str_remove( colnames(pY_noNA), "log2FC_Xenograft_" )
pY_noNA %>% select()
Return_DEP_Hits_Plots(data = pY_noNA , 
                      dep_ctrl_vs_E_pY, 
                      comparison = "E_vs_ctrl_diff")

Return_DEP_Hits_Plots(data = pY_noNA , 
                      dep_ctrl_vs_E_pY, 
                      comparison = "E_vs_ctrl_diff")
```

```{r}
data_diff_EC_vs_ctrl_pY <- test_diff(pY_se_prep2, type="manual", test = "EC_vs_ctrl")
dep_EC_vs_ctrl_pY <- add_rejections_SH(data_diff_EC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_ctrl_pY, contrast = "EC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff")
```

```{r, eval=FALSE}
Plot_Enrichment_Single_Pathway(dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff", 
                               pw = "Epigenetic regulation of gene expression")
```

```{r}
data_diff_EBC_vs_ctrl_pY <- test_diff(pY_se_prep2, type="manual", test = "EBC_vs_ctrl")
dep_EBC_vs_ctrl_pY <- add_rejections_SH(data_diff_EBC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_ctrl_pY, contrast = "EBC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_ctrl_pY, comparison = "EBC_vs_ctrl_diff")
```

#### EC vs E
```{r}
data_diff_EC_vs_E_pY <- test_diff(pY_se_prep2, type = "manual", 
                              test = c("EC_vs_E"))
dep_EC_vs_E_pY <- add_rejections_SH(data_diff_EC_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_E_pY, contrast = "EC_vs_E", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_E_pY, comparison = "EC_vs_E_diff")

#data_results <- get_df_long(dep)
```

#### EBC vs EC
```{r}
data_diff_EBC_vs_EC_pY <- test_diff(pY_se_prep2, type = "manual", 
                              test = c("EBC_vs_EC"))
dep_EBC_vs_EC_pY <- add_rejections_SH(data_diff_EBC_vs_EC_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_EC_pY, contrast = "EBC_vs_EC", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_EC_pY, comparison = "EBC_vs_EC_diff")

#data_results <- get_df_long(dep)
```


### Tyrosine 24h
#### Each condition vs ctrl
```{r, eval=TRUE}
pY_se_24h <- pY_se

pY_se_24h <- pY_se_24h[,pY_se_24h$day == "24h" | (pY_se_24h$day == "5d" & pY_se_24h$condition == "ctrl")]

data_diff_ctrl_vs_E_pY <- test_diff(pY_se_24h, type="manual", test = "E_vs_ctrl")
dep_ctrl_vs_E_pY <- add_rejections_SH(data_diff_ctrl_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_ctrl_vs_E_pY, contrast = "E_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_ctrl_vs_E_pY, comparison = "E_vs_ctrl_diff")
```

```{r}
data_diff_EC_vs_ctrl_pY <- test_diff(pY_se_24h, type="manual", test = "EC_vs_ctrl")
dep_EC_vs_ctrl_pY <- add_rejections_SH(data_diff_EC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_ctrl_pY, contrast = "EC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff")
```

```{r, eval=FALSE}
Plot_Enrichment_Single_Pathway(dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff", 
                               pw = "Epigenetic regulation of gene expression")
```

```{r}
data_diff_EBC_vs_ctrl_pY <- test_diff(pY_se_24h, type="manual", test = "EBC_vs_ctrl")
dep_EBC_vs_ctrl_pY <- add_rejections_SH(data_diff_EBC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_ctrl_pY, contrast = "EBC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_ctrl_pY, comparison = "EBC_vs_ctrl_diff")
```


#### Not ctrl vs ctrl
```{r, eval=FALSE}
data_diff_vs_ctrl_pY <- test_diff_to_all_other(pY_se_24h, control = "ctrl")
dep_vs_ctrl_pY <- add_rejections_SH(data_diff_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_vs_ctrl_pY, contrast = "not_ctrl_vs_ctrl", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10, eval=FALSE}
Return_DEP_Hits_Plots(data = pY_noNA, dep_vs_ctrl_pY, comparison = "not_ctrl_vs_ctrl_diff")
```

#### EC vs E
```{r}
data_diff_EC_vs_E_pY <- test_diff(pY_se_24h, type = "manual", 
                              test = c("EC_vs_E"))
dep_EC_vs_E_pY <- add_rejections_SH(data_diff_EC_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_E_pY, contrast = "EC_vs_E", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_E_pY, comparison = "EC_vs_E_diff")

#data_results <- get_df_long(dep)
```

#### EBC vs EC
```{r}
data_diff_EBC_vs_EC_pY <- test_diff(pY_se_24h, type = "manual", 
                              test = c("EBC_vs_EC"))
dep_EBC_vs_EC_pY <- add_rejections_SH(data_diff_EBC_vs_EC_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_EC_pY, contrast = "EBC_vs_EC", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_EC_pY, comparison = "EBC_vs_EC_diff")

#data_results <- get_df_long(dep)
```

#### Preps
```{r}
pY_se_24h_preps <- pY_se_24h

pY_se_24h_preps$treatment <- pY_se_24h_preps$condition
pY_se_24h_preps$prep <- unlist(prep_l[paste0("Xenograft_", rownames(colData(pY_se_24h_preps)) )])
pY_se_24h_preps_comp <- pY_se_24h_preps
pY_se_24h_preps_comp$condition <- pY_se_24h_preps$prep

data_diff_prep1_vs_prep2_pY <- test_diff(pY_se_24h_preps_comp, type = "manual", 
                              test = c("prep1_vs_prep2"))
dep_prep1_vs_prep2_pY <- add_rejections_SH(data_diff_prep1_vs_prep2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_prep1_vs_prep2_pY, contrast = "prep1_vs_prep2", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_prep1_vs_prep2_pY, comparison = "prep1_vs_prep2_diff")

#data_results <- get_df_long(dep)
```

#### Runs
```{r}
pY_se_24h_runs <- pY_se_24h

pY_se_24h_runs$treatment <- pY_se_24h_runs$condition
pY_se_24h_runs$run <- str_split(colnames(pY_se_24h_runs), pattern = "_", simplify = TRUE)[,4]
pY_se_24h_runs_comp <- pY_se_24h_runs
pY_se_24h_runs_comp$condition <- pY_se_24h_runs$run

data_diff_Set1_vs_Set2_pY <- test_diff(pY_se_24h_runs_comp, type = "manual", 
                              test = c("Set1_vs_Set2"))
dep_Set1_vs_Set2_pY <- add_rejections_SH(data_diff_Set1_vs_Set2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_Set1_vs_Set2_pY, contrast = "Set1_vs_Set2", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_Set1_vs_Set2_pY, comparison = "Set1_vs_Set2_diff")

#data_results <- get_df_long(dep)
```


### Tyrosine 5d
#### Each condition vs ctrl
```{r, eval=TRUE}
pY_se_5d <- pY_se

pY_se_5d <- pY_se_5d[,pY_se_5d$day == "5d" ]

data_diff_ctrl_vs_E_pY <- test_diff(pY_se_5d, type="manual", test = "E_vs_ctrl")
dep_ctrl_vs_E_pY <- add_rejections_SH(data_diff_ctrl_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_ctrl_vs_E_pY, contrast = "E_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_ctrl_vs_E_pY, comparison = "E_vs_ctrl_diff")
```

```{r}
data_diff_EC_vs_ctrl_pY <- test_diff(pY_se_5d, type="manual", test = "EC_vs_ctrl")
dep_EC_vs_ctrl_pY <- add_rejections_SH(data_diff_EC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_ctrl_pY, contrast = "EC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff")
```

```{r, eval=FALSE}
Plot_Enrichment_Single_Pathway(dep_EC_vs_ctrl_pY, comparison = "EC_vs_ctrl_diff", 
                               pw = "Epigenetic regulation of gene expression")
```

```{r}
data_diff_EBC_vs_ctrl_pY <- test_diff(pY_se_5d, type="manual", test = "EBC_vs_ctrl")
dep_EBC_vs_ctrl_pY <- add_rejections_SH(data_diff_EBC_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_ctrl_pY, contrast = "EBC_vs_ctrl", 
                label_size = 2, add_names = TRUE,
                additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_ctrl_pY, comparison = "EBC_vs_ctrl_diff")
```


#### Not ctrl vs ctrl
```{r, eval=FALSE}
data_diff_vs_ctrl_pY <- test_diff_to_all_other(pY_se_5d, control = "ctrl")
dep_vs_ctrl_pY <- add_rejections_SH(data_diff_vs_ctrl_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_vs_ctrl_pY, contrast = "not_ctrl_vs_ctrl", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10, eval=FALSE}
Return_DEP_Hits_Plots(data = pY_noNA, dep_vs_ctrl_pY, comparison = "not_ctrl_vs_ctrl_diff")
```

#### EC vs E
```{r}
data_diff_EC_vs_E_pY <- test_diff(pY_se_5d, type = "manual", 
                              test = c("EC_vs_E"))
dep_EC_vs_E_pY <- add_rejections_SH(data_diff_EC_vs_E_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EC_vs_E_pY, contrast = "EC_vs_E", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EC_vs_E_pY, comparison = "EC_vs_E_diff")

#data_results <- get_df_long(dep)
```

#### EBC vs EC
```{r}
data_diff_EBC_vs_EC_pY <- test_diff(pY_se_5d, type = "manual", 
                              test = c("EBC_vs_EC"))
dep_EBC_vs_EC_pY <- add_rejections_SH(data_diff_EBC_vs_EC_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_EBC_vs_EC_pY, contrast = "EBC_vs_EC", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_EBC_vs_EC_pY, comparison = "EBC_vs_EC_diff")

#data_results <- get_df_long(dep)
```

#### Preps
```{r}
pY_se_5d_preps <- pY_se_5d

pY_se_5d_preps$treatment <- pY_se_5d_preps$condition
pY_se_5d_preps$prep <- unlist(prep_l[paste0("Xenograft_", rownames(colData(pY_se_5d_preps)) )])
pY_se_5d_preps_comp <- pY_se_5d_preps
pY_se_5d_preps_comp$condition <- pY_se_5d_preps$prep

data_diff_prep1_vs_prep2_pY <- test_diff(pY_se_5d_preps_comp, type = "manual", 
                              test = c("prep1_vs_prep2"))
dep_prep1_vs_prep2_pY <- add_rejections_SH(data_diff_prep1_vs_prep2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_prep1_vs_prep2_pY, contrast = "prep1_vs_prep2", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_prep1_vs_prep2_pY, comparison = "prep1_vs_prep2_diff")

#data_results <- get_df_long(dep)
```

#### Runs
```{r}
pY_se_5d_runs <- pY_se_5d

pY_se_5d_runs$treatment <- pY_se_5d_runs$condition
pY_se_5d_runs$run <- str_split(colnames(pY_se_5d_runs), pattern = "_", simplify = TRUE)[,4]
pY_se_5d_runs_comp <- pY_se_5d_runs
pY_se_5d_runs_comp$condition <- pY_se_5d_runs$run

data_diff_Set1_vs_Set2_pY <- test_diff(pY_se_5d_runs_comp, type = "manual", 
                              test = c("Set1_vs_Set2"))
dep_Set1_vs_Set2_pY <- add_rejections_SH(data_diff_Set1_vs_Set2_pY, alpha = 0.05, lfc = log2(1.2))
GGPlotly_Wrapper_Volcano(plot_volcano_SH(dep_Set1_vs_Set2_pY, contrast = "Set1_vs_Set2", label_size = 2, add_names = TRUE, additional_title = "pY"))
```

```{r, fig.width=10, fig.height=10}
Return_DEP_Hits_Plots(data = pY_noNA, dep_Set1_vs_Set2_pY, comparison = "Set1_vs_Set2_diff")

#data_results <- get_df_long(dep)
```


# Session Info
```{r}
sessionInfo()
knitr::knit_exit()
```
