---
title: "Quality control - Distributions - DIPG Batch 1"
author: Sophie Herbst
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
Analysis date: `r Sys.Date()`

# Depends on
CRC_Xenografts_FirstBatch_DataProcessing Script

```{r}
load("../Data/Cache/Xenografts_Batch1_DataProcessing.RData")
```

# TODO


# Setup
## Load libraries and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(2022)
library(fgsea)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(DEP)
library(SummarizedExperiment)
# library(pls)
library(mdatools)
source("../../../General/Code/Analysis_Functions.R")
source("CRC_Xenografts_Batch1_Functions.R")
```

# Quality control
## Nr. phospho sites
```{r}
print( paste( nrow(pY_Set1) , "pY peptides passed the filtering procedure for Set 1. These peptides were detected from", length(unique(pY_Set1$HGNC_Symbol) ), "proteins." ))
#print( paste( nrow(pST_Set1) , "pST peptides passed the filtering procedure for Set 1. These peptides were detected from", length(unique(pST$HGNC_Symbol) ), "proteins." ))

print( paste( nrow(pY_Set2) , "pY peptides passed the filtering procedure for Set 2. These peptides were detected from", length(unique(pY_Set2$HGNC_Symbol) ), "proteins." ))
#print( paste( nrow(pST_Set2) , "pST peptides passed the filtering procedure for Set 2. These peptides were detected from", length(unique(pST$HGNC_Symbol) ), "proteins." ))

print( paste( nrow(pY_Set3) , "pY peptides passed the filtering procedure for Set 2. These peptides were detected from", length(unique(pY_Set3$HGNC_Symbol) ), "proteins." ))

print( paste( nrow(pY_noNA) , "pY peptides passed the filtering procedure for the sets combined. These peptides were detected from", length(unique(pY_noNA$HGNC_Symbol) ), "proteins." ))
#print( paste( nrow(pST_noNA) , "pST peptides passed the filtering procedure for the sets combined. These peptides were detected from", length(unique(pST_noNA$HGNC_Symbol) ), "proteins." ))
```

## Nr. proteins whole proteome
```{r, eval=FALSE}
print( paste( length(unique(prot_Set1$HGNC_Symbol) ), "proteins detected in Set 1." ))
print( paste( length(unique(prot_Set2$HGNC_Symbol) ), "proteins detected in Set 2." ))

print( paste( length(unique(prot_top3peptidemedian$HGNC_Symbol) ), "proteins detected in both Sets." ))
```

## Distributions
### pY Abundances
#### Set 1
```{r}
pY_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pY_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pY_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pY_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

pY_Set1 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Set 2
```{r}
pY_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pY_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pY_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pY_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

pY_Set2 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Set 3
```{r}
pY_Set3 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pY_Set3 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pY_Set3 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pY_Set3 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

pY_Set3 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Combined
##### Colored by treatment
```{r}
pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_"), drop = F) %>%
  separate( Sample , into = c("xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  ggplot(aes(value, fill= treatment, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  ggplot(aes(Sample, value, fill= treatment)) +
  geom_boxplot() +
  ggtitle("log2FC to normal") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  group_by(Sample, treatment, day, replicate, set) %>%
  summarise(mean_value = mean(value)) %>%
  ggplot(aes(treatment, mean_value, fill= treatment)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])
```

##### Colored by day
```{r}
pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_"), drop = F) %>%
  separate( Sample , into = c("xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  ggplot(aes(value, fill= day, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  group_by(Sample, treatment, day, replicate, set) %>%
  summarise(mean_value = mean(value)) %>%
  ggplot(aes(day, mean_value, fill= day)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  group_by(Sample, treatment, day, replicate, set) %>%
  summarise(mean_value = mean(value)) %>%
  ggplot(aes(day, mean_value, fill= day)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)]) +
  facet_grid(~treatment)
```

##### Colored by Prep
```{r}
pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_"), drop = F) %>%
  separate( Sample , into = c("xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  mutate(prep = unlist(prep_l[Sample] )) %>%
  ggplot(aes(value, fill= prep, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  mutate(prep = unlist(prep_l[Sample] )) %>%
  group_by(Sample, treatment, day, replicate, set, prep) %>%
  summarise(mean_value = mean(value)) %>%
  ggplot(aes(prep, mean_value, fill= prep)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])


pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  mutate(prep = unlist(prep_l[Sample] )) %>%
  group_by(Sample, treatment, day, replicate, set, prep) %>%
  summarise(mean_value = mean(value)) %>%
  #filter(treatment == "ctrl") %>%
  ggplot(aes(prep, mean_value, fill= prep)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)]) +
  facet_grid(day~treatment)
```



##### Colored by Set
```{r}
pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_"), drop = F) %>%
  separate( Sample , into = c("xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  ggplot(aes(value, fill= set, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pY_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate( Sample , into = c( "xenograft", "treatment", "day", "replicate", "set"), sep = "_", remove = F) %>%
  group_by(Sample, treatment, day, replicate, set) %>%
  summarise(mean_value = mean(value)) %>%
  ggplot(aes(set, mean_value, fill= set)) +
  geom_boxplot() +
  ggbeeswarm::geom_beeswarm() +
  ggtitle("log2FC to normal") +
  ggpubr::stat_compare_means() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

```


### pST Abundances
#### Set 1
```{r, eval=FALSE}
pST_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pST_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pST_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pST_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

pST_Set1 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Set 2
```{r, eval=FALSE}
pST_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pST_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pST_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pST_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

pST_Set2 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Combined
```{r, eval=FALSE}
pST_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate(Sample, into = c("treatment", "replicate"), remove = F) %>%
  ggplot(aes(value, fill= treatment, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)]) +
  geom_vline(xintercept = 0)

pST_noNA %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate(Sample, into = c("treatment", "replicate"), remove = F) %>%
  ggplot(aes(Sample, value, fill= treatment)) +
  geom_boxplot() +
  ggtitle("log2FC to bridge") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_manual(values = PGPalette[c(1, 2, 4, 5)])

pST_noNA %>%
  select(contains("log2FC")) %>%
  select(!contains("normal")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate(Sample, into = c("treatment", "replicate"), remove = F) %>%
  ggplot(aes(value, fill= treatment, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 5)])
```

### Whole proteome abundances
#### Set 1
```{r, eval=FALSE}
prot_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  geom_density(alpha=0.5) +
  xlim(0,10e5) +
  ggtitle("Raw abundances")

prot_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10) +
  ggtitle("Abundances normalised to sup")

prot_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

prot_Set1 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

prot_Set1 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Set 2
```{r, eval=FALSE}
prot_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e5) +
  ggtitle("Raw abundances")

prot_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10) +
  ggtitle("Abundances normalised to sup")

prot_Set2 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

prot_Set2 %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")

prot_Set2 %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to bridge")
```

#### Combined
```{r, eval=FALSE}
prot_top3peptidemedian %>%
  select(contains("log2FC")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal")

prot_top3peptidemedian %>%
  select(contains("log2FC")) %>%
  select(!contains("normal")) %>%
  pivot_longer(names_to = "Sample", cols = everything()) %>%
  mutate(Sample = str_remove(Sample, "log2FC_")) %>%
  separate(Sample, into = c("treatment", "replicate"), remove = F) %>%
  ggplot(aes(value, fill= treatment, group = Sample)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("log2FC to normal") +
  theme_bw() +
  scale_fill_manual(values = PGPalette[c(1, 2, 5)])

t(pST_mat_nonormal) %>%
  as.data.frame(  ) %>%
  rownames_to_column( "peptide") %>%
  pivot_longer(-peptide, names_to = "sample", values_to = "log2FC") %>%
  mutate(sample = gsub( "log2FC_", "", sample)) %>%
  separate(sample, into = c("treatment", "replicate"), sep = "-",remove = F)   %>%
  separate(peptide, into = c("HGNC_Symbol", "Annotated_Sequence"), sep =   "_", remove = F ) %>%
  group_by(sample, treatment, replicate) %>%
  summarise("Mean of patient" = mean(log2FC)) %>%
  ungroup() %>%
  mutate(treatment = as.factor(treatment)) %>%
  mutate(treatment = factor(treatment, levels = c("WT", "G34R", "K27M"))) %>%
  ggplot(aes( treatment, `Mean of patient`, fill = treatment )) +
  geom_boxplot(outlier.size = 0) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90),
  axis.title.x = element_blank()) +
  scale_fill_manual(values = PGPalette[c(5,1,2)]) +
  ggbeeswarm::geom_beeswarm() +
  ggpubr::stat_compare_means(method = "t.test",
  comparisons = list(c("WT", "G34R"),
  c("WT", "K27M"),
  c("K27M", "G34R")) ) +
  ggtitle("pST median normalised log2 fold change")

```

### pY Mean-Variance Relationship
#### Set 1
```{r}
pY_Set1 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  group_by(peptide) %>%
  summarise(mean = mean(value), sd = sd (value) ) %>%
  ggplot(aes(mean, sd)) +
  xlim(0,10e4) +
  ylim(0,10e4) +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")

pY_Set1 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  mutate(log2value = log2(value) ) %>%
  group_by(peptide) %>%
  summarise(meanlog2 = mean(log2value), sdlog2 = sd (log2value) ) %>%
  ggplot(aes(meanlog2, sdlog2)) +
  #ylim(0,10e4) +
  #scale_x_log10() +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")
```

#### Set 2
```{r}
pY_Set2 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  group_by(peptide) %>%
  summarise(mean = mean(value), sd = sd (value) ) %>%
  ggplot(aes(mean, sd)) +
  xlim(0,10e4) +
  ylim(0,10e4) +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")

pY_Set2 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  mutate(log2value = log2(value) ) %>%
  group_by(peptide) %>%
  summarise(meanlog2 = mean(log2value), sdlog2 = sd (log2value) ) %>%
  ggplot(aes(meanlog2, sdlog2)) +
  #ylim(0,10e4) +
  #scale_x_log10() +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")
```

#### Set 3
```{r}
pY_Set3 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  group_by(peptide) %>%
  summarise(mean = mean(value), sd = sd (value) ) %>%
  ggplot(aes(mean, sd)) +
  xlim(0,10e4) +
  ylim(0,10e4) +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")

pY_Set3 %>%
  mutate(peptide = paste0( HGNC_Symbol, "_", `Annotated Sequence` )) %>%
  select(peptide, contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = -peptide) %>%
  mutate(log2value = log2(value) ) %>%
  group_by(peptide) %>%
  summarise(meanlog2 = mean(log2value), sdlog2 = sd (log2value) ) %>%
  ggplot(aes(meanlog2, sdlog2)) +
  #ylim(0,10e4) +
  #scale_x_log10() +
  #geom_histogram(bins= 200) +
  geom_point() +
  ggtitle("pY sd vs. mean") +
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")
```

### pY Abundances per peptide
#### Set 1
```{r}
pY_Set1 %>%
  select(contains("Abundance"), -contains("TMT")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")
```

# Session Info
```{r}
sessionInfo()
knitr::knit_exit()
```
