---
title: "CRC - Xenografts batch1 Set1"
author: Sophie Herbst
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

Analysis date: `r Sys.Date()`

# Setup
## Load libraries and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("../../../General/Code/Analysis_Functions.R")
```

```{r}
plot_centered_pheatmap_around_1 <- function(val_pmap){
  br <- seq( -( max(abs( min(val_pmap)), abs(max(val_pmap))) ) , ( max(abs( min(val_pmap)), abs(max(val_pmap))) + 2 ), 0.1 )
  br <- br[ min(sum( br < min(val_pmap) ) , sum(br > max(val_pmap) ) ) : ( length(br) - min(sum( br < min(val_pmap) ) , sum(br > max(val_pmap) ) ) ) ]
  val_pmap %>% 
    pheatmap::pheatmap(col = colorRampPalette(c("navy", "white", "firebrick3"))(length(br)), breaks = br)
}
```

## File paths
```{r, warning=FALSE}
set.seed(2022)
file_path_pY <- "../Data/Mass_Spec/SH_20221207_CRC_Xenografts_Batch1_Set1_TMTPro_AC49_AA_pY2_PSMs.txt"
#file_path_pST <- "Data/Mass_Spec/SH_20221006_Sepsis_MACSlowvolume_TMT10_AC39_AA_pST_PSMs.txt"
file_path_sup <- "../Data/Mass_Spec/SH_20221207_CRC_Xenografts_Batch1_Set1_TMTpro_pre6+AC46_HR1-50min_sup_PSMs.txt"
```


## Process data
```{r, warning=FALSE}
pY <- Filter_And_Average_PSMs(file_path_phos = file_path_pY,  row_center_phos = TRUE,
                              file_path_sup = file_path_sup, 
                              return_data = "phos",  NA_cutoff_channel = 0.4,
                              NA_replace = FALSE, NA_peptide_cutoff = 0,
                              ion_score_filter = 20) %>%
    filter(grepl("y", `Annotated Sequence` ) )

pY_raw <- pY

#pST <- Filter_And_Average_PSMs(file_path_phos = file_path_pST, row_center_phos = TRUE,
#                              file_path_sup = file_path_sup,
#                              return_data = "phos", 
#                              NA_replace = FALSE, NA_peptide_cutoff = 0, NA_cutoff_channel = 0.05,
#                              ion_score_filter = 10) %>%
#  filter(grepl("s|t", `Annotated Sequence` ) )
#pST_raw <- pST
```

## Format data
### Annotate
```{r}
name_l = list( "126" = "Xenograft_EBC_24h_1",
               "127N" = "Xenograft_ctrl_5d_6",
               "127C" = "Xenograft_E_24h_4",
               "128N"	= "Xenograft_ctrl_5d_3",
               "128C"	 = "Xenograft_EC_24h_1",
               "129N"	= "Xenograft_EBC_24h_2",
               "129C"	= "Xenograft_ctrl_5d_2",
               "130N"	= "Xenograft_E_24h_3",
               "130C"	= "Xenograft_EBC_24h_3",
               "131N"	= "Xenograft_E_24h_1",
               "131C"	= "Xenograft_EC_24h_2",
               "132N"	= "Xenograft_E_24h_2",
               "132C"	= "Xenograft_ctrl_5d_7",
               "133N"	= "Xenograft_EC_24h_3",
               "133C"	= "Xenograft_ctrl_5d_5",
               "134N"= "Xenograft_ctrl_5d_1"
)
  

prep_l = list( "Xenograft_EBC_24h_1" = "prep1" ,
               "Xenograft_ctrl_5d_6"= "prep2",
               "Xenograft_E_24h_4"= "prep2",
               "Xenograft_ctrl_5d_3" = "prep1",
               "Xenograft_EC_24h_1"= "prep1",
               "Xenograft_EBC_24h_2"= "prep1",
               "Xenograft_ctrl_5d_2" = "prep2",
               "Xenograft_E_24h_3"= "prep1",
               "Xenograft_EBC_24h_3"= "prep2",
               "Xenograft_E_24h_1"= "prep1",
               "Xenograft_EC_24h_2"= "prep2",
               "Xenograft_E_24h_2"= "prep1",
               "Xenograft_ctrl_5d_7" = "prep1",
               "Xenograft_EC_24h_3"= "prep2",
               "Xenograft_ctrl_5d_5" = "prep1",
               "Xenograft_ctrl_5d_1" = "prep1"
               )

seppack_l = list( "Xenograft_EBC_24h_1" = "seppack1" ,
               "Xenograft_ctrl_5d_6"= "seppack2",
               "Xenograft_E_24h_4"= "seppack1",
               "Xenograft_ctrl_5d_3" = "seppack1",
               "Xenograft_EC_24h_1"= "seppack1",
               "Xenograft_EBC_24h_2"= "seppack2",
               "Xenograft_ctrl_5d_2" = "seppack1",
               "Xenograft_E_24h_3"= "seppack2",
               "Xenograft_EBC_24h_3"= "seppack1",
               "Xenograft_E_24h_1"= "seppack1",
               "Xenograft_EC_24h_2"= "seppack1",
               "Xenograft_E_24h_2"= "seppack2",
               "Xenograft_ctrl_5d_7" = "seppack2",
               "Xenograft_EC_24h_3"= "seppack2",
               "Xenograft_ctrl_5d_5" = "seppack2",
               "Xenograft_ctrl_5d_1" = "seppack1"
               )
```

### Log2 Transform
```{r}
pY <- pY_raw %>% 
  Minimize_df(name_l = name_l) %>%
  mutate_at(vars(contains("Xenograft")), function(x) log2(x))

#pST <- pST_raw %>% 
#  Minimize_df(name_l = name_l) %>%
#  mutate_at(vars(contains("neutrophils")), function(x) log2(x))
```

### Matrix
```{r}
pY_mat <- pY_raw %>% 
  Minimize_df(name_l = name_l) %>%
  select(-HGNC_Symbol, -Annotated_Sequence) %>%
  as.matrix() %>% 
  t()

colnames(pY_mat) <- paste0( pY_raw$HGNC_Symbol, "_", pY_raw$`Annotated Sequence` )

#pST_mat <- pST_raw %>% 
#  Minimize_df(name_l = name_l) %>%
#  select(-HGNC_Symbol, -Annotated_Sequence) %>%
#  as.matrix() %>% 
#  t()
#
#colnames(pST_mat) <- paste0( pST_raw$HGNC_Symbol, "_", pST_raw$`Annotated Sequence` )
```

# Quality control
## Nr. phospho sites
```{r}
print( paste( nrow(pY) , "pY peptides passed the filtering procedure. These peptides were detected from", length(unique(pY$HGNC_Symbol) ), "proteins." ))

#print( paste( nrow(pST) , "pST peptides passed the filtering procedure. These peptides were detected from", #length(unique(pST$HGNC_Symbol) ), "proteins." ))
```

## Distributions
### pY Abundances
```{r}
pY_raw %>%
  select(contains("Abundance"), -contains("TMT"), -contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pY_raw %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pY_raw %>%
  select(contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("Centered abundances")

pY_raw %>%
  select(contains("Abundance"), -contains("TMT"), -contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pY_raw %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")
```

### pST Abundances
```{r, eval=FALSE}
pST_raw %>%
  select(contains("Abundance"), -contains("TMT"), -contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Raw abundances")

pST_raw %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  xlim(0,10e4) +
  ggtitle("Abundances normalised to sup")

pST_raw %>%
  select(contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  ggtitle("Centered abundances")

pST_raw %>%
  select(contains("Abundance"), -contains("TMT"), -contains("Centered_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Raw abundances")

pST_raw %>%
  select(contains("TMTNorm_Abundance")) %>%
  pivot_longer(names_to = "Channel", cols = everything()) %>%
  ggplot(aes(value, fill= Channel)) +
  #geom_histogram(bins= 200) +
  geom_density(alpha=0.5) +
  scale_x_log10() +
  ggtitle("Abundances normalised to sup")
```

## Principle component analysis
### Phospho-Tyrosines
```{r, fig.width=3, fig.height=3}
pY_mat %>%
  prcomp() %>% 
  summary() %>% 
  .$importance %>% t() %>% as.data.frame() %>%
  rownames_to_column("PC") %>% 
  as_tibble() %>%
  mutate(PC = as.factor(PC)) %>%
  mutate(PC = factor(PC, levels = PC)) %>%
  ggplot(aes(PC, `Proportion of Variance` )) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r, fig.width=9, fig.height=3}
PCA_pY <- pY_mat %>%
  prcomp() %>% 
  .$x %>% 
  as.data.frame() %>%
  rownames_to_column("sample")

PCApY_rot <- pY_mat %>%
  prcomp() %>%
  .$rotation
PCApY_rot <- bind_cols(PCApY_rot, 
  (pY_raw %>% 
    Minimize_df(name_l = name_l) %>%
    select(HGNC_Symbol, Annotated_Sequence) ) ) %>% arrange(desc(PC1) )

PCA_pY$prep <- unlist(prep_l[PCA_pY$sample])
PCA_pY$seppack <- unlist(seppack_l[PCA_pY$sample])

PCA_pY <- PCA_pY %>% 
  separate(sample, into = c("Xenograft", "treatment", "day", "replicate"), sep = "_")

PCA12_pY <- PCA_pY %>% 
  ggplot(aes(PC1, PC2, color = treatment, shape = day )) +
  geom_point(size = 3) +
  theme_classic() +
  #scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pY")

PCA34_pY <- PCA_pY %>% 
  ggplot(aes(PC3, PC4, color = treatment, shape = day )) +
  geom_point(size = 3) +
  theme_classic() +
  #scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pY")

ggpubr::ggarrange(PCA12_pY, PCA34_pY)

PCA12_pY <- PCA_pY %>% 
  ggplot(aes(PC1, PC2, color = prep, shape = seppack )) +
  geom_point(size = 3) +
  theme_classic() +
  #scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pY")

PCA34_pY <- PCA_pY %>% 
  ggplot(aes(PC3, PC4, color = prep, shape = seppack )) +
  geom_point(size = 3) +
  theme_classic() +
  #scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pY")

ggpubr::ggarrange(PCA12_pY, PCA34_pY)
```

These are the weights of the peptides loaded onto the principle components:

```{r, fig.width=4, fig.height=3}
DT::datatable( PCApY_rot, 
              class = 'cell-border stripe', rownames = FALSE) %>% 
  DT::formatRound(c('PC1', 'PC2', 'PC3', 'PC4', 'PC5', 'PC6'), 3)
```

### Phospho-Serines and Phospho-Threonines
```{r, fig.width=3, fig.height=3, eval=FALSE}
pST_mat %>%
  prcomp() %>% 
  summary() %>% 
  .$importance %>% t() %>% as.data.frame() %>%
  rownames_to_column("PC") %>% 
  as_tibble() %>%
  mutate(PC = as.factor(PC)) %>%
  mutate(PC = factor(PC, levels = PC)) %>%
  ggplot(aes(PC, `Proportion of Variance` )) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r, fig.width=9, fig.height=3, eval=FALSE}
PCA_pST <- pST_mat %>%
  prcomp() %>% 
  .$x %>% 
  as.data.frame() %>%
  rownames_to_column("sample")

PCApST_rot <- pST_mat %>%
  prcomp() %>%
  .$rotation
PCApST_rot <- bind_cols(PCApST_rot, 
  (pST_raw %>% 
    Minimize_df(name_l = name_l) %>%
    select(HGNC_Symbol, Annotated_Sequence) ) ) %>% arrange(desc(PC1) )

PCA_pST <- PCA_pST %>% 
  separate(sample, into = c("cells", "condition", "Volume", "replicate"), sep = "_")

PCA12_pST <- PCA_pST %>% 
  ggplot(aes(PC1, PC2, color = condition, shape = replicate )) +
  geom_point(size = 3) +
  theme_classic() +
  scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pS/pT")

PCA34_pST <- PCA_pST %>% 
  ggplot(aes(PC3, PC4, color = condition, shape = replicate )) +
  geom_point(size = 3) +
  theme_classic() +
  scale_colour_manual(values=PGPalette[c(1,5)]) +
  #geom_text(aes(label = replicate), color = "black", nudge_x = 1) +
  ggtitle("pS/pT")

ggpubr::ggarrange(PCA12_pST, PCA34_pST)
```

These are the weights of the peptides loaded onto the principle components:

```{r, fig.width=4, fig.height=3, eval=FALSE}
DT::datatable( PCApST_rot, 
              class = 'cell-border stripe', rownames = FALSE) %>% 
  DT::formatRound(c('PC1', 'PC2', 'PC3', 'PC4', 'PC5', 'PC6'), 3)
```

## Correlation between samples
```{r}
psych::corPlot(pY[, 3:18], scale = FALSE, diag = TRUE, upper = FALSE, zlim = c(0, 1 ), 
               main = "Correlation samples pY", xlas =2, labels =  colnames(pY[, 3:18]) ) 

#psych::corPlot(pST[, 3:8], scale = FALSE, diag = TRUE, upper = FALSE, zlim = c(0, 1 ), 
#               main = "Correlation samples pST", xlas =2, labels =  colnames(pST[, 3:8]) ) 
```

# Analysis
## Heatmaps
### Phospho-Tyrosines
#### Clustered
```{r, fig.height=8, fig.width=4}
pY_raw %>% 
  Minimize_df(name_l = name_l, centered = TRUE ) %>%
  select(-HGNC_Symbol, -Annotated_Sequence) %>%
  as.matrix() %>%
  plot_centered_pheatmap_around_1
```

### Phospho-Serines and Phospho-Threonines
#### Clustered
```{r, fig.height=8, fig.width=4, eval=FALSE}
pST %>% 
  select(-HGNC_Symbol, -Annotated_Sequence) %>%
  as.matrix() %>%
  pheatmap::pheatmap(col = colorRampPalette(c("navy", "white", "firebrick3"))(50))

pST_centered_tmp <- pST_raw %>% 
  Minimize_df(name_l = name_l, centered = TRUE )
pST_centered_tmp[,-c(1,2)][pST_centered_tmp[,-c(1,2)] >2] <- 2
pST_centered_tmp %>%  
  select(-HGNC_Symbol, -Annotated_Sequence) %>%
  as.matrix() %>%
  pheatmap::pheatmap(col = colorRampPalette(c("navy", "white", "firebrick3"))(50))
```

## Searchable tables
### Phospho-Tyrosines
```{r}
DT::datatable( pY, 
              class = 'cell-border stripe', rownames = FALSE, 
              colnames = colnames(pY)) %>% DT::formatRound(colnames(pY)[3:18], 3)
```

### Phospho-Serines and Phospho-Threonines
```{r, eval=FALSE}
DT::datatable( pST, 
              class = 'cell-border stripe', rownames = FALSE, 
              colnames = colnames(pST)) %>% DT::formatRound(colnames(pST)[3:8], 3)
```

# Conclusion

# Session Info
```{r}
sessionInfo()
knitr::knit_exit()
```
