---
title: "Quality control correlations - DIPG Batch 1"
author: Sophie Herbst
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
Analysis date: `r Sys.Date()`

# Depends on
DIPG_FirstBatch_DataProcessing Script

```{r}
load("../Data/Cache/DIPG_FirstBatch_DataProcessingMissingValues40.RData")
```

# TODO
# Setup
## Load libraries and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(2022)
library(fgsea)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(DEP)
library(SummarizedExperiment)
# library(pls)
library(mdatools)
source("../../../General/Code/Analysis_Functions.R")
source("DIPG_FirstBatch_Functions.R")
```

# Quality control
## Correlation between samples
```{r}


psych::corPlot(pY[, grep("log2FC", colnames(pY) )], scale = FALSE, diag = TRUE, upper = FALSE, zlim = c(0, 1 ), 
               main = "Correlation samples pY", xlas =2, labels = gsub( "log2FC_", "", colnames(pY[, grep("log2FC", colnames(pY) )]) ) )

psych::corPlot(pST[, grep("log2FC", colnames(pST) )], scale = FALSE, diag = TRUE, upper = FALSE, zlim = c(0, 1 ), 
               main = "Correlation samples pST", xlas =2,  labels = gsub( "log2FC_", "", colnames(pST[, grep("log2FC", colnames(pST) )]) ) )

psych::corPlot(prot[, grep("log2FC", colnames(prot) )], scale = FALSE, diag = TRUE, upper = FALSE, zlim = c(0, 1 ), 
               main = "Correlation samples whole proteome", xlas =2,  labels = gsub( "log2FC_", "", colnames(prot[, grep("log2FC", colnames(prot) )]) ) )
```

## Correlation between peptides
### Phospho-Tyrosines 
```{r, fig.width=10, fig.height=10}
corr_mat_pY <- round(cor(pY_mat),2)
 
# reorder corr matrix
# using corr coefficient as distance metric
dist_pY <- as.dist((1-corr_mat_pY)/2)
 
# hierarchical clustering the dist matrix
hc_pY <- hclust(dist_pY)
plot(as.dendrogram(hc_pY))
#rect.hclust(hc, k = 8)
corr_mat_pY <-corr_mat_pY[hc_pY$order, hc_pY$order]
 
# reduce the size of correlation matrix
melted_corr_mat_pY <- reshape2::melt(corr_mat_pY)
#head(melted_corr_mat)
 
#plotting the correlation heatmap
ggplot(data = melted_corr_mat_pY, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_continuous(type = "viridis") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(size = 2.5))
```

### Phospho-Serines/Threonines 
```{r, fig.width=10, fig.height=10}
corr_mat_pST <- round(cor(pST_mat),2)
 
# reorder corr matrix
# using corr coefficient as distance metric
dist_pST <- as.dist((1-corr_mat_pST)/2)
 
# hierarchical clustering the dist matrix
hc_pST <- hclust(dist_pST)
plot(as.dendrogram(hc_pST))
#rect.hclust(hc, k = 8)
corr_mat_pST <-corr_mat_pST[hc_pST$order, hc_pST$order]
 
# reduce the size of correlation matrix
melted_corr_mat_pST <- reshape2::melt(corr_mat_pST)
#head(melted_corr_mat)
 
#plotting the correlation heatmap
ggplot(data = melted_corr_mat_pST, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_continuous(type = "viridis") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(size = 2.5))
```

### Phospho-Tyrosines and Phospho-Serines/Threonines combined
```{r, fig.width=10, fig.height=10}
overlap_pats <- intersect(rownames(pY_mat), rownames(pST_mat) )
stopifnot(rownames(pST_mat[overlap_pats,]) == rownames(pY_mat[overlap_pats,]) )
corr_mat_pYpST <- round(cor(cbind(pY_mat[overlap_pats,], pST_mat[overlap_pats,])),2)
 
# reorder corr matrix
# using corr coefficient as distance metric
dist_pYpST <- as.dist((1-corr_mat_pYpST)/2)
 
# hierarchical clustering the dist matrix
hc_pYpST <- hclust(dist_pYpST)
plot(as.dendrogram(hc_pYpST))
#rect.hclust(hc, k = 8)
corr_mat_pYpST <-corr_mat_pYpST[hc_pYpST$order, hc_pYpST$order]
 
# reduce the size of correlation matrix
melted_corr_mat_pYpST <- reshape2::melt(corr_mat_pYpST)
#head(melted_corr_mat)
 
#plotting the correlation heatmap
ggplot(data = melted_corr_mat_pYpST, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_continuous(type = "viridis") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(size = 2.5))
```
 
### No normal Phospho-Tyrosines and Phospho-Serines/Threonines combined
#### Heatmap
```{r, fig.width=10, fig.height=10}
pST_mat_nonormal <- pST_mat[!grepl("normal", rownames(pST_mat)),]
pY_mat_nonormal <- pY_mat[!grepl("normal", rownames(pY_mat)),]
overlap_pats <- intersect(rownames(pY_mat_nonormal), rownames(pST_mat_nonormal) )
stopifnot(rownames(pST_mat_nonormal[overlap_pats,]) == rownames(pY_mat_nonormal[overlap_pats,]) )

corr_mat_pYpST_nonormal <- round(cor(cbind(pY_mat_nonormal[overlap_pats,], pST_mat_nonormal[overlap_pats,])),2)
 
# reorder corr matrix
# using corr coefficient as distance metric
dist_pYpST_nonormal <- as.dist((1-corr_mat_pYpST_nonormal)/2)
 
# hierarchical clustering the dist matrix
hc_pYpST_nonormal <- hclust(dist_pYpST_nonormal)
plot(as.dendrogram(hc_pYpST_nonormal))
#rect.hclust(hc, k = 8)
corr_mat_pYpST_nonormal <-corr_mat_pYpST_nonormal[hc_pYpST_nonormal$order, hc_pYpST_nonormal$order]
 
# reduce the size of correlation matrix
melted_corr_mat_pYpST_nonormal <- reshape2::melt(corr_mat_pYpST_nonormal)
#head(melted_corr_mat)
 
#plotting the correlation heatmap
ggplot(data = melted_corr_mat_pYpST_nonormal, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_continuous(type = "viridis") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(size = 2.5))
```



# Session Info
```{r}
sessionInfo()
knitr::knit_exit()
```
