---
title: "PLSDA - DIPG Batch 1"
author: Sophie Herbst
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
Analysis date: `r Sys.Date()`

# Depends on
DIPG_FirstBatch_DataProcessing Script

```{r}
load("../Data/Cache/DIPG_FirstBatch_DataProcessingMissingValues40.RData")
```

# TODO

* Find out whether I need to vsn
* Look at raw data from bridge channel
* Where do the missing values in whole proteome data come from?
* Whole proteome: Normalise abundances by total proteome abundance mean: did I do it correctly or do I have to mean center first?
* Match BBB and PKIDB properly
* Understand PLSDA results

# Setup
## Load libraries and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(2022)
library(fgsea)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(DEP)
library(SummarizedExperiment)
# library(pls)
library(mdatools)
library(mixOmics)
source("../../../General/Code/Analysis_Functions.R")
source("DIPG_FirstBatch_Functions.R")
```

## Functions
### PLSDA
```{r}
Tune_And_Perform_PLSDA <- function(X, Y, folds, repeats, scale = TRUE, upperlimitfeatures = 200, initial_nr_of_components = 10, progressBar = TRUE){
  plsda <- splsda( X = X, 
         Y= Y, scale = scale, ncomp = initial_nr_of_components)

    message("Done calculating initial PLSDA")
  message("Tuning components:")
  perf.plsda <- perf(plsda, validation = "Mfold", 
                            folds = folds, nrepeat = repeats, # use repeated cross-validation
                            progressBar = progressBar, auc = TRUE) # include AUC values
  plot(perf.plsda, col = color.mixo(5:7), 
       sd = TRUE,
       legend.position = "horizontal")
  #perf.plsda$choice.ncomp
  message("Done tuning components")
  
  # grid of possible keepX values that will be tested for each component
  list.keepX <- c(1:20,  seq(20, upperlimitfeatures, 10))
  
  message("Tune number of selected features:")
  # undergo the tuning process to determine the optimal number of variables
  tune.plsda <- tune.splsda(X = X, Y= Y, scale = scale,
         ncomp = perf.plsda$choice.ncomp[2,1], validation = 'Mfold',
         folds = folds, nrepeat = repeats, # use repeated cross-validation
         dist = 'max.dist', # use max.dist measure
         measure = "BER", # use balanced error rate of dist measure
         test.keepX = list.keepX,
         progressBar = progressBar,
         cpus = 2) 
  p_tune_feat <- plot(tune.plsda, col = color.jet(perf.plsda$choice.ncomp[2,1]))
  print(p_tune_feat)
  message(paste("Optimal number of components:", tune.plsda$choice.ncomp$ncomp ) )
  message("Optimal number of selected features per component:")
  print(tune.plsda$choice.keepX)
  optimal.ncomp <- tune.plsda$choice.ncomp$ncomp
  optimal.keepX <- tune.plsda$choice.keepX[1:optimal.ncomp]
  
  message("Calculate final sPLSDA model")
  final.splsda <- splsda(X, Y, 
                         ncomp = optimal.ncomp, 
                         keepX = optimal.keepX, scale = scale)
#  perf.final.splsda <- perf(final.splsda, 
#                          folds = folds, nrepeat = repeats, # use #repeated cross-validation
#                          validation = "Mfold", dist = "max.dist",  # #use max.dist measure
#                          progressBar = FALSE, auc = TRUE)
#  perf.final.splsda$auc
  return(final.splsda)
}
```

### GSEA
```{r}
Run_GSEA_PLSDA <- function(PLSDA_result, component){
  ranked_list <- 
    PLSDA_result$loadings$X %>% 
    as.data.frame() %>%
    rownames_to_column("peptide") %>%
    as_tibble() %>%
    separate(peptide, into = c("HGNC_Symbol", "Annotated_Sequence")) %>%
    select(HGNC_Symbol, FC = {{ component }} ) %>% 
    mutate(absFC = abs(FC) ) %>%
    group_by(HGNC_Symbol) %>%
    arrange(desc(absFC) ) %>%
    slice(1) %>%
    ungroup %>%
    arrange(FC)
  
  ranked_vector <- unlist(ranked_list[,2])
  names(ranked_vector) <- mapIds(org.Hs.eg.db, 
                                 keys = ranked_list$HGNC_Symbol,
                                 column = "ENTREZID", keytype = "SYMBOL")
  
  ranked_vector <- ranked_vector[!is.na(names(ranked_vector)) ]
  
  pathways <- reactomePathways(names(ranked_vector))
  fgseaRes <- fgsea(pathways, ranked_vector, maxSize=500)
  
  #print(head(fgseaRes))
  
  topPathwaysUp <- fgseaRes[ES > 0 & padj < 0.1][head(order(pval), n=10), pathway]
  topPathwaysDown <- fgseaRes[ES < 0 & padj < 0.1][head(order(pval), n=10), pathway]
  topPathways <- c(topPathwaysUp, rev(topPathwaysDown))
  message(paste( length(topPathways), "pathways below FDR of 10%"))
  if(length(topPathways) > 0 ){
    plot.new()
    ggplot() + theme_void()
    plotGseaTable(pathways[topPathways], ranked_vector, fgseaRes, 
                  gseaParam=0.5)
  }
}
```

# Analyses
## Partial least squares discriminat analysis

### Without normal
#### pY
##### Perform PLSDA
```{r plsda_nonormal_pY}
plsda_pY_nonormal <- Tune_And_Perform_PLSDA(
  X = pY_mat_nonormal_normtomedian,
  Y = as.factor( str_split( gsub("log2FC_", "", rownames( pY_mat_nonormal_normtomedian ) ), 
         pattern = "-", simplify = TRUE )[,1] ),
  repeats = 50, folds = 3, initial_nr_of_components = 4,
  scale = TRUE, progressBar = FALSE)
```

##### Plot Components
```{r}

plotIndiv(plsda_pY_nonormal, comp = c(1,2), # plot samples from final model
          col.per.group = PGPalette[c(1,2,5)],
          ellipse = TRUE, legend = TRUE, # include 95% confidence ellipse
          title = ' (a) sPLS-DA on pY, comp 1 & 2')

plsda_pY_nonormal$prop_expl_var
```

##### Plot Loadings
```{r, fig.height=7}
plotLoadings(plsda_pY_nonormal, method = 'mean', contrib = 'max', comp = 1, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])    
plotLoadings(plsda_pY_nonormal, method = 'mean', contrib = 'max', comp = 2, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])   
#plotLoadings(plsda_pY_nonormal, method = 'mean', contrib = 'max', comp = 3, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])  
```

##### Correlation Circle Plot
```{r}
plotVar(plsda_pY_nonormal, cex =2, comp = c(1,2), var.names =  list(stringr::str_split(plsda_pY_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#plotVar(plsda_pY_nonormal, cex =2, comp = c(2,3), var.names =  list(stringr::str_split(plsda_pY_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#selectVar(plsda_pY_nonormal, comp = 1)$name 
```

##### GSEA
```{r}
Run_GSEA_PLSDA(PLSDA_result = plsda_pY_nonormal, component = comp1)
Run_GSEA_PLSDA(PLSDA_result = plsda_pY_nonormal, component = comp2)
```

##### StringDB
```{r}
Plot_StringDB(
  rownames(plsda_pY_nonormal$loadings$X[ (plsda_pY_nonormal$loadings$X[,1] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
Plot_StringDB(
  rownames(plsda_pY_nonormal$loadings$X[ (plsda_pY_nonormal$loadings$X[,2] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
```

#### pST
##### Perform PLSDA
```{r plsda_nonormal_pST}
plsda_pST_nonormal <- Tune_And_Perform_PLSDA(
  X = pST_mat_nonormal_normtomedian,
  Y = as.factor( str_split( gsub("log2FC_", "", rownames( pST_mat_nonormal_normtomedian ) ), 
         pattern = "-", simplify = TRUE )[,1] ),
  repeats = 50, folds = 3, initial_nr_of_components = 4,
  scale = TRUE, progressBar = FALSE)
```

##### Plot Components
```{r}

plotIndiv(plsda_pST_nonormal, comp = c(1,2), # plot samples from final model
          col.per.group = PGPalette[c(1,2,5)],
          ellipse = TRUE, legend = TRUE, # include 95% confidence ellipse
          title = ' (a) sPLS-DA on pST, comp 1 & 2')

plsda_pST_nonormal$prop_expl_var
```

##### Plot Loadings
```{r, fig.height=7}
plotLoadings(plsda_pST_nonormal, method = 'mean', contrib = 'max', comp = 1, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])    
plotLoadings(plsda_pST_nonormal, method = 'mean', contrib = 'max', comp = 2, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])   
#plotLoadings(plsda_pST_nonormal, method = 'mean', contrib = 'max', comp = 3, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])  
```

##### Correlation Circle Plot
```{r}
plotVar(plsda_pST_nonormal, cex =2, comp = c(1,2), var.names =  list(stringr::str_split(plsda_pST_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#plotVar(plsda_pST_nonormal, cex =2, comp = c(2,3), var.names =  #list(stringr::str_split(plsda_pST_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#selectVar(plsda_pST_nonormal, comp = 1)$name 
```

##### GSEA
```{r}
Run_GSEA_PLSDA(PLSDA_result = plsda_pST_nonormal, component = comp1)
Run_GSEA_PLSDA(PLSDA_result = plsda_pST_nonormal, component = comp2)
```

##### StringDB
```{r}
Plot_StringDB(
  rownames(plsda_pST_nonormal$loadings$X[ (plsda_pST_nonormal$loadings$X[,1] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
Plot_StringDB(
  rownames(plsda_pST_nonormal$loadings$X[ (plsda_pST_nonormal$loadings$X[,2] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
```

####  pY and pST combined
##### Perform PLSDA
```{r plsda_nonormal_pY_pST}
overlap_pat <- intersect(rownames(pST_mat_nonormal_normtomedian), rownames(pY_mat_nonormal_normtomedian))
stopifnot(rownames(pST_mat_nonormal_normtomedian[overlap_pat,]) == rownames(pY_mat_nonormal_normtomedian[overlap_pat,]) )
mat_pYpST_nonormal <- cbind(pY_mat_nonormal_normtomedian[overlap_pat,], pST_mat_nonormal_normtomedian[overlap_pat,])

plsda_pYpST_nonormal <- Tune_And_Perform_PLSDA(
  X = mat_pYpST_nonormal[,!duplicated(colnames(mat_pYpST_nonormal))], 
  Y = as.factor( str_split(gsub("log2FC_", "", rownames( mat_pYpST_nonormal ) ), 
         pattern = "-", simplify = TRUE )[,1] ),  
  repeats = 50, folds = 3, initial_nr_of_components = 5,
  scale = TRUE, progressBar = FALSE)
```

##### Plot Components
```{r}

plotIndiv(plsda_pYpST_nonormal, comp = c(1,2), # plot samples from final model
          col.per.group = PGPalette[c(1,2,5)],
          ellipse = TRUE, legend = TRUE, # include 95% confidence ellipse
          title = ' (a) sPLS-DA on pY and pST, comp 1 & 2')

plsda_pYpST_nonormal$prop_expl_var
```

##### Plot Loadings
```{r, fig.height=7}
plotLoadings(plsda_pYpST_nonormal, method = 'mean', contrib = 'max', comp = 1, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])    
plotLoadings(plsda_pYpST_nonormal, method = 'mean', contrib = 'max', comp = 2, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])   
#plotLoadings(plsda_pYpST_nonormal, method = 'mean', contrib = 'max', comp = 3, size.name = 0.5, size.title = 1, legend.color = PGPalette[c(1,2,5)])  
```

##### Correlation Circle Plot
```{r}
plotVar(plsda_pYpST_nonormal, cex =2, comp = c(1,2), var.names =  list(stringr::str_split(plsda_pYpST_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#plotVar(plsda_pYpST_nonormal, cex =2, comp = c(2,3), var.names =  list(stringr::str_split(plsda_pYpST_nonormal$names$colnames$X, pattern = "_", simplify = T )[,1] ) )
#selectVar(plsda_pYpST_nonormal, comp = 1)$name 
```

##### GSEA
```{r, eval=FALSE}
Run_GSEA_PLSDA(PLSDA_result = plsda_pYpST_nonormal, component = comp1)
Run_GSEA_PLSDA(PLSDA_result = plsda_pYpST_nonormal, component = comp2)
```

##### StringDB
```{r}
Plot_StringDB(
  rownames(plsda_pYpST_nonormal$loadings$X[ (plsda_pYpST_nonormal$loadings$X[,1] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
Plot_StringDB(
  rownames(plsda_pYpST_nonormal$loadings$X[ (plsda_pYpST_nonormal$loadings$X[,2] != 0 ),] ) %>% 
  str_split(pattern = "_", simplify = T) %>% .[,1])
```

# Session Info
```{r}
sessionInfo()
knitr::knit_exit()
```
